pyg4ometry: a python library for the creation of Monte Carlo particle transport geometries

### 2019-03-07 paper/pyg4ometry.tex
Small edits
Small tweeks

\subsection{Tessellation engine}
For each Geant4 primitive solid a triangular tessellated mesh is generated and cached. This mesh is then used to determine the extent of placed instances of 
geometry (physical volumes) and meshes for CSG derived solids. CSG mesh calculations are performed using a BSP tree technique. Triangular meshes based
on CSG operations involving curved surfaces often contain large numbers of thin triangles. Before meshes are visualised or written to disk various algorithms from 
TetGEN can be employed to give the meshes more desirable output.

\subsection{Internal data representation} 
The internal data representation follows closely the structure of GDML. A \verb|Registry| class aggregates python ordered dictionaries that are  used to store the main 
elements of a GDML file. As a user specifies geometry the registry is updated. When a user is finished with the geometry, the registry is written to disk as a GDML file.

@@

@@

@@

>>>>

\subsection{Tessellation engine}
For each Geant4 primitive solid a triangular tessellated mesh is generated and cached. This mesh is then used to determine the extent of placed instances of 
geometry (physical volumes) and meshes for CSG derived solids. CSG mesh calculations are performed using a BSP tree technique. Triangular meshes based
on CSG operations involving curved surfaces often contain large numbers of thin triangles. Before meshes are visualised or written to disk various algorithms from 
TetGEN can be employed to give the meshes more desirable features.

\subsection{Replica, parametrised and looped volumes}
A powerful feature of Geant4 and hence GDML is the ability to either repeat or parametrise geometry. The create mulitple replicas of a volume in a cartesian, cylindrical or 
spherical grid is known as a ReplicaVolume.

\subsection{Internal data representation} 
The internal data representation follows closely the structure of GDML. A \verb|Registry| class aggregates python ordered dictionaries that are  used to store the main 
elements of a GDML file. As a user specifies geometry the registry is updated. When a user is finished with the geometry, the registry is written to disk as a GDML file.
\verb|Registry| instances can be aggregated to form a composite geometry or volumes can be removed and added.

@@

\subsection{Volume bounding} 
If a user is creating a placing multiple {\em daughter} volumes within a {\em mother} volume then it is the users responsibility to create a solid which fully encompasses the 
daughter volumes. Overlaps between daughter volumes and the mother can be detected, but it is desirable to have a mother volume shape that efficiently holds all of its daughters.

@@

\subsection{Adding properties to volumes}
A pure geometry description is an insufficient description for a PT simulation. Often other attributes need to be assigned for example material definition, magnetic field or

\subsection{Graphical user interface}
A basic Qt based graphical user interface is also available with pyg4ometry. If a model has a large number of volumes defined in a hierarchical tree structure, it is cumbersome for the user to find the logical or physical volume.

@@

\section{Interesting use cases}
pyg4ometry is designed to be as flexible as possible and offer the user a wide range of usage styles and workflows. The following sections describe a selection of 
possible applications.

\subsection{Mixing geometry sources}
It is possible to mix different geometries from STL, STEP, GDML and FLUKA in single GDML file for use in Geant4 and ROOT.

\subsection{Editing existing CAD models}
Often existing CAD models have either missing details or too much detail.

\subsection{Overlap checking in geometry}
Often small errors in geometry cause unexpected PT code behaviour.
